Type Refinements for the Working Class

### 2015-11-20 paper.tex
fix notation

Now, we can extend $R_\tau$ to a new relation $[R_\tau]$ on closed expressions
which respects a single ``layer'' of computation. We will say
$\SBinRel{[R_\tau]}{\Upsilon}{M}{N}$ when, supposing
$\Eval{\Upsilon}{\tau}{M}{\App{\vartheta}{\Vec{E}}}$ such that
$\Lookup{\CanOperators}{\vartheta}{\MkArity{\vec{v}}{\tau}}$, for any
$\Of{\rho}{\Upsilon\inj\Upsilon'}$, we have
$\Eval{\Upsilon'}{\tau}{N\rho}{\App{\vartheta\rho}{\Vec{F}\rho}}$ and
$\SBinRel{R_{\vec{v}}}{\Upsilon'}{\vec{E}\rho}{\vec{F}\rho}$.

>>>>

Now, we can extend $R_\tau$ to a new relation $[R_\tau]$ on closed expressions
which respects a single ``layer'' of computation. We will say
$\SBinRel{[R_\tau]}{\Upsilon}{M}{N}$ when, supposing
$\Eval{\Upsilon}{\tau}{M}{\App{\vartheta}{\Vec{E}}}$ such that
$\IMode{\Upsilon}\Vdash_{\IMode{\CanOperators}}\IMode{\vartheta}:\OMode{\MkArity{\vec{v}}{\tau}}$,
for any $\Of{\rho}{\Upsilon\inj\Upsilon'}$, we have
$\Eval{\Upsilon'}{\tau}{N\rho}{\App{\vartheta\rho}{\Vec{F}\rho}}$ and
$\SBinRel{R_{\vec{v}}}{\Upsilon'}{\vec{E}\rho}{\vec{F}\rho}$.
